\epigraph{None of us get out of here alive.}{Jim Morrison of the Doors}
\epigraph{Political language ... is designed to make lies sound truthful and murder respectable, and to give an appearance of solidity to pure wind.}{George Orwell}
\epigraph{I never let my schooling get in the way of my education.}{Mark Twain}
\epigraph{Leave death nothing but a burnt out castle.}{Zorba The Greek}
\epigraph{Not afraid of math. It just has a terrible ROI compared to many things that I don't have time for either.}{Henrik Vendelbo}
\epigraph{Thinking is necessary in order to understand the empirically given, and concepts and “categories” are necessary as indispensable elements of thinking}{A. Einstein, 1949, Reply to criticism}
\epigraph{... it is impossible to explain honestly the beauties of the laws of nature in a way that people can feel, without their having some deep understanding of mathematics. I am sorry, but this seems to be the case.}{Richard Feynman}
\epigraph{Even God wouldn't get a grant today because somebody on the committee would say, oh those were very interesting experiments (creating the universe), but they've never been repeated. And then someone else would say, yes and he did it a long time ago; what's he done recently? And a third would say, to top it all, he published it all in an un-refereed journal (The Bible).}{Sydney Brenner}
\epigraph{Certainly the best times were when I was alone with mathematics, free of ambition and pretense, and indifferent to the world.}{Langlands, in Mathematicians: An Outer View of the Inner World}      
\epigraph{Do not work within two hours of a substantial meal; blood cannot be in two places at once.}{J.E. Littlewood, in Littlewood's miscellany, p199.}
                